Methods for Large Scale Learning to Rank

### 2014-09-25 report/Chapters/Background.tex
mapreduce kort uitgelegd

\section{An introduction to the MapReduce programming model}
TODO

>>>>

\section{An introduction to the MapReduce programming model}
MapReduce \cite{Dean2004} is a programming model invented at Google, where users specify a \emph{map} function that processes a key/value pair to generate a set of intermediate key/value pairs, and a \emph{reduce} function that merges all intermediate values associated with the same intermediate key. This model draws its inspiration from the field of functional programming, where \emph{map} and \emph{reduce} are commonly used functions.\\

This combination of the \emph{map} and \emph{reduce} functions allows for parallel computation. In the \emph{map} phase parallel computation can be performed by simply splitting the input data after a certain number of bytes, where each worker nodes performs the user-specified \emph{map}-function on its share of the data. Before the \emph{reduce} phase these intermediate answers of the different worker nodes are transformed in such a way that they are grouped by key value, this is called the shuffle-phase. After the shuffle-phase, the user-defined \emph{reduce}-function is applied to each group of key/value pairs in the reduce phase. Since the key/value pairs are already grouped by key in the shuffle phase, this \emph{reduce}-function can be applied to a group of key/value pairs on any of the worker nodes.\\
